\documentclass{article}

\title{Maser's thesis outline}
\author{Jonas Folkvord Triki}

\begin{document}
\maketitle

\setcounter{section}{-1}
\section{Abstract}
In this section, I will briefly introduce my thesis question, mention what methods are going to be used (Neural networks, word2vec, etc.) and quickly what kind of analysis I'm going to do in this thesis.

\section{Introduction}
In this section, I am first going to introduce word embeddings and some history behind it (why it is used, where it started, etc.). Following, I will give some classical examples of it's usage and mention where it is used as of today. I will also give a quick introduction to all the methods used in this thesis.

\section{Word embeddings}
In this section, I will first dig deeper into the word2vec method for computing word embeddings. I will explore it's different architectures and will implement a simple model to create word embeddings of texts from both the Norwegian and English language. I then compare my results to check for language differences.

I might also take a look at other methods other than word2vec for computing such word embeddings.

I will also use some pre-trained networks (already existing weights) to test on my set of texts.

\section{Analysis of embeddings}
In this section, I will analyze my results from the previous section. I will use unsupervised methods such as dimensionality reduction (PCA, UMAP, TSNE, etc.) and clustering (K-means, Agglomerative, Spectral, HDBSCAN, etc.). I will also visualize my results and discuss my results (word embeddings of English vs. Norwegian).

\section{Topological analysis}
In this section, I will perform some hypothesis testing using topological methods (Vietoris-Rips/Čech complexes, persistence diagrams, etc.). In particular, I would like to see if words like "north, south, west, east" form a circle. I will also look into unsupervised hypothesis testing and look for topological properties of word embeddings in general. I will also like to see if one could improve training of neural networks by using topological properties found from word embeddings.

\section{Conclusion}
In this section, I will conclude with my results and discuss briefly what findings I have.

\section{Bibliography}
In this section, I will list all the sources I have used in the process of writing this thesis.

\end{document}